
This qmd is a culmination from `00-04`. I hope that I was able to tell a story on how we're approaching this problem.

We will first define a function that encompasses all the important parts needed to do one simulation run, and then we will run our simulations *(potentially in different documents to avoid confusion, but we're not sure at the moment)*.

`repeat_full_simulation` is a function that calculates (most of) the performance of all four methods of interest. This is a very extensive function and is what everything has built up to.

```{r}
repeat_full_simulation <- function() {
  
  # STEP 0) Define datasets for all four methods
  CC_total_result <- data.frame()
  CD_total_result <- data.frame()
  PMM_total_result <- data.frame()
  CLQI_total_result <- data.frame()
  
  #have an iteration indicator to see if function is still running
  iteration_indicator <- 0

  
}
```

> "Test case": See that everything generates for all four methods

```{r}

```


# SIMULATION SETTING 1: 

```{r}

```

